\rule{\textwidth}{4pt}\\[0.5cm] \textbf{Payout profile approximation with vanilla European options}\\[0.5cm] \rule{\textwidth}{2pt}

### 2025-02-02 latex/article.tex
renaming
keywords

\title{\rule{\textwidth}{2pt}\\[0.5cm]
\textbf{Payout profile approximation with vanilla European options}\\[0.5cm]
\rule{\textwidth}{1pt}}
\author{\small \textbf{Vlad Kochetov} \\
    \small Faculty of Mechanics and Mathematics, \\
    \small Taras Shevchenko National University of Kyiv \\
    \small \texttt{vladkoch@knu.ua}
}
\date{\today}

@@

\begin{abstract}
This paper explores the methodology for approximating complex payout profiles using a combination of vanilla European options. We present a mathematical framework that allows for the decomposition of arbitrary payout structures into a series of call and put options with varying strike prices. The approach is validated through numerical examples and practical applications in financial engineering. The results demonstrate the effectiveness of this method in replicating complex payouts with high accuracy while maintaining computational efficiency.
\end{abstract}

\keywords{Vanilla Options, 
          Payout Profile, 
          Financial Engineering, 
          Option Pricing, 
          Approximation,
          Numerical Methods}

\section{Introduction}
The ability to replicate complex financial instruments using simpler, more liquid derivatives is a cornerstone of modern financial engineering. Vanilla European options, due to their simplicity and widespread availability, serve as ideal building blocks for such approximations. This paper introduces a novel approach to approximating arbitrary payout profiles using a combination of these options.

>>>>

\title{\rule{\textwidth}{4pt}\\[0.5cm]
\textbf{Payout profile approximation with vanilla European options}\\[0.5cm]
\rule{\textwidth}{2pt}}
\author{\small \textbf{Vlad Kochetov} \\
    \small Faculty of Mechanics and Mathematics, \\
    \small Taras Shevchenko National University of Kyiv \\
    \small \texttt{vladkoch@knu.ua}
}
\date{\today}

@@

\begin{abstract}
This paper explores the methodology for approximating complex payout profiles using a combination of vanilla European options. The mathematical framework is presented that allows for the decomposition of arbitrary payout structures into a series of call and put options with varying strike prices. The approach is validated through numerical examples and practical applications in financial engineering. The results demonstrate the effectiveness of this method in replicating complex payouts with high accuracy while maintaining computational efficiency.
\end{abstract}

\keywords{
    \small{
        Vanilla Options, 
        Payout Profile, 
        Financial Engineering, 
        Option Pricing, 
        Approximation, 
        Numerical Methods,
        Quantitative Finance,
        Financial Derivatives,
        Computational Finance
    }
}

\section{Introduction}
The ability to replicate complex financial instruments using simpler, more liquid derivatives is a cornerstone of modern financial engineering. Vanilla European options, due to their simplicity and widespread availability, serve as ideal building blocks for such approximations. This paper introduces an approach to approximating arbitrary payout profiles using a combination of these options.
